Figure 5 - IP-MS

### 2024-08-07 ms_figure_2_overview-heatmaps.Rmd
Small clean-up of heatmap functions

```{r extract-heatmap-data-ipms}
hmdata_150 <- makeHeatmapData(sce = sce150, adjpthr = adjpThreshold, 
                              log2fcthr = log2fcThreshold, conc = 150)
hmdata_500 <- makeHeatmapData(sce = sce500, adjpthr = adjpThreshold, 
                              log2fcthr = log2fcThreshold, conc = 500)
```

@@

hm1a <- Heatmap(hmdata_150$tstat, 
                cluster_rows = FALSE, 
                cluster_columns = FALSE, 
                col = makeHeatmapCol(stringency = "high"), 
                border = TRUE, 
                border_gp = gpar(lwd = 0.5),
                column_split = hmdata_150$colsplit, 
                name = "Mod. t-stat.", 
                na_col = binary_heatmap_colors["FALSE"],
                column_names_gp = gpar(fontsize = fs),
                row_names_gp = gpar(fontsize = fs),
                row_title = "Proteins significantly enriched in at least one experiment",
                row_title_gp = gpar(fontsize = fl),
                show_row_names = FALSE, show_column_names = FALSE,
                use_raster = FALSE, show_heatmap_legend = TRUE,
                right_annotation = makeComplexAnnotation(
                    hmdata_150$tstat, complexes[complexLabel], 
                    idmap = idmap),
                bottom_annotation = makeColLabels(hmdata_150$tstat, colLabel_150, fl),
                width = unit(w_ipmsHm, "mm"), # heatmap body width
                heatmap_height = unit(h_ipmsHm, "mm"), # whole heatmap height
                column_title_gp = gpar(fontsize = ft),
                heatmap_legend_param = list(title_gp = gpar(fontsize = fl), 
                                            legend_direction = "horizontal",
                                            title_position = "topcenter",
                                            border = "gray10",
                                            border_gp = gpar(lwd = 0.5)))

@@

hm2a <- Heatmap(hmdata_500$tstat, 
                cluster_rows = FALSE, 
                cluster_columns = FALSE, 
                col = makeHeatmapCol(stringency = "high"), 
                border = TRUE, 
                border_gp = gpar(lwd = 0.5),
                column_split = hmdata_500$colsplit, 
                name = "Mod. t-stat.", 
                na_col = binary_heatmap_colors["FALSE"],
                column_names_gp = gpar(fontsize = fs),
                row_names_gp = gpar(fontsize = fs),
                row_title = "Proteins significantly enriched in at least one experiment",
                row_title_gp = gpar(fontsize = fl),
                show_row_names = FALSE, show_column_names = FALSE,
                use_raster = FALSE, show_heatmap_legend = TRUE,
                right_annotation = makeComplexAnnotation(hmdata_500$tstat, complexes[complexLabel],
                                                         idmap = idmap, show_legend = FALSE),
                bottom_annotation = makeColLabels(hmdata_500$tstat, colLabel_500, fl),
                width = unit(w_ipmsHm, "mm"), # heatmap body width
                heatmap_height = unit(h_ipmsHm, "mm"), # whole heatmap height
                column_title_gp = gpar(fontsize = ft),
                heatmap_legend_param = list(title_gp = gpar(fontsize = fl), 
                                            legend_direction = "horizontal",
                                            title_position = "topcenter",
                                            border = "gray10",
                                            border_gp = gpar(lwd = 0.5)))

>>>>

```{r extract-heatmap-data-ipms}
hmdata_150 <- makeHeatmapData(sce = sce150, adjpthr = adjpThreshold, 
                              log2fcthr = log2fcThreshold, conc = 150,
                              idmap = idmap, baitclass = baitclass)
hmdata_500 <- makeHeatmapData(sce = sce500, adjpthr = adjpThreshold, 
                              log2fcthr = log2fcThreshold, conc = 500,
                              idmap = idmap, baitclass = baitclass)
```

@@

hm1a <- Heatmap(hmdata_150$tstat, 
                cluster_rows = FALSE, 
                cluster_columns = FALSE, 
                col = makeHeatmapCol(stringency = "high"), 
                border = TRUE, 
                border_gp = gpar(lwd = 0.5),
                column_split = hmdata_150$colsplit, 
                name = "Mod. t-stat.", 
                na_col = binary_heatmap_colors["FALSE"],
                column_names_gp = gpar(fontsize = fs),
                row_names_gp = gpar(fontsize = fs),
                row_title = "Proteins significantly enriched in at least one experiment",
                row_title_gp = gpar(fontsize = fl),
                show_row_names = FALSE, show_column_names = FALSE,
                use_raster = FALSE, show_heatmap_legend = TRUE,
                right_annotation = makeComplexAnnotation(
                    hmdata_150$tstat, complexes[complexLabel], 
                    idmap = idmap, show_legend = TRUE, fontsize = fl, bg_color = bg_color),
                bottom_annotation = makeColLabels(hmdata_150$tstat, colLabel_150, fl),
                width = unit(w_ipmsHm, "mm"), # heatmap body width
                heatmap_height = unit(h_ipmsHm, "mm"), # whole heatmap height
                column_title_gp = gpar(fontsize = ft),
                heatmap_legend_param = list(title_gp = gpar(fontsize = fl), 
                                            legend_direction = "horizontal",
                                            title_position = "topcenter",
                                            border = "gray10",
                                            border_gp = gpar(lwd = 0.5)))

@@

hm2a <- Heatmap(hmdata_500$tstat, 
                cluster_rows = FALSE, 
                cluster_columns = FALSE, 
                col = makeHeatmapCol(stringency = "high"), 
                border = TRUE, 
                border_gp = gpar(lwd = 0.5),
                column_split = hmdata_500$colsplit, 
                name = "Mod. t-stat.", 
                na_col = binary_heatmap_colors["FALSE"],
                column_names_gp = gpar(fontsize = fs),
                row_names_gp = gpar(fontsize = fs),
                row_title = "Proteins significantly enriched in at least one experiment",
                row_title_gp = gpar(fontsize = fl),
                show_row_names = FALSE, show_column_names = FALSE,
                use_raster = FALSE, show_heatmap_legend = TRUE,
                right_annotation = makeComplexAnnotation(
                    hmdata_500$tstat, complexes[complexLabel],
                    idmap = idmap, show_legend = FALSE, fontsize = fl, bg_color = bg_color),
                bottom_annotation = makeColLabels(hmdata_500$tstat, colLabel_500, fl),
                width = unit(w_ipmsHm, "mm"), # heatmap body width
                heatmap_height = unit(h_ipmsHm, "mm"), # whole heatmap height
                column_title_gp = gpar(fontsize = ft),
                heatmap_legend_param = list(title_gp = gpar(fontsize = fl), 
                                            legend_direction = "horizontal",
                                            title_position = "topcenter",
                                            border = "gray10",
                                            border_gp = gpar(lwd = 0.5)))

### 2024-08-07 ms_figure_5_ipms.Rmd
Small clean-up of heatmap functions

```{r extract-heatmap-data}
hmdata_150 <- makeHeatmapData(sce = sce150, adjpthr = adjpThreshold, 
                              log2fcthr = log2fcThreshold, conc = 150)
hmdata_150_loose <- makeHeatmapData(sce = sce150, adjpthr = adjpThresholdLoose, 
                                    log2fcthr = log2fcThreshold, conc = 150)
hmdata_500 <- makeHeatmapData(sce = sce500, adjpthr = adjpThreshold, 
                              log2fcthr = log2fcThreshold, conc = 500)
hmdata_500_loose <- makeHeatmapData(sce = sce500, adjpthr = adjpThresholdLoose, 
                                    log2fcthr = log2fcThreshold, conc = 500)

baitdata_150 <- makeBaitHeatmapData(sce = sce150, adjpthr = adjpThreshold, 
                                    log2fcthr = log2fcThreshold, 
                                    nbrIntMat = hmdata_150$nbrIntMat)
baitdata_150_loose <- makeBaitHeatmapData(sce = sce150, adjpthr = adjpThresholdLoose, 
                                          log2fcthr = log2fcThreshold, 
                                          nbrIntMat = hmdata_150_loose$nbrIntMat)
baitdata_500 <- makeBaitHeatmapData(sce = sce500, adjpthr = adjpThreshold, 
                                    log2fcthr = log2fcThreshold, 
                                    nbrIntMat = hmdata_500$nbrIntMat)
baitdata_500_loose <- makeBaitHeatmapData(sce = sce500, adjpthr = adjpThresholdLoose, 
                                          log2fcthr = log2fcThreshold, 
                                          nbrIntMat = hmdata_500_loose$nbrIntMat)
```

@@

hm1b <- Heatmap(baitdata_150$mat, 
                cluster_rows = FALSE, 
                cluster_columns = FALSE, 
                col = makeHeatmapCol(stringency = "high"), 
                border = TRUE, 
                border_gp = gpar(lwd = 0.5),
                name = "Mod.\nt-stat.", 
                na_col = binary_heatmap_colors["FALSE"],
                column_title = paste(c("150 mM NaCl IP-MS", rep(" ", 45)), collapse = ""),
                row_title = "Transcription factors",
                column_title_gp = gpar(fontsize = fl + 3, fontface = "bold"),
                row_title_gp = gpar(fontsize = fl),
                column_names_gp = gpar(fontsize = fs),
                row_names_gp = gpar(fontsize = fs),
                show_row_names = FALSE, show_column_names = FALSE,
                use_raster = FALSE, show_heatmap_legend = TRUE, 
                left_annotation = makeComplexAndDBDAnnotation(
                    baitdata_150$mat, 
                    complexes[c("MBF transcription complex", 
                                "CCAAT-binding factor complex",
                                "Atf1-Pcr1")],
                    dbd = dbd, 
                    idmap = idmap),
                top_annotation = makeTFIntAnnotation(baitdata_150), 
                bottom_annotation = makeColLabels(baitdata_150$mat, 
                                                  c("Ntu1_plate", "Ntu2_plate", 
                                                    "Esc1_tube", "SPAC3F10.12c_plate"), fl),
                width = unit(w_ipmsHm, "mm") / 1.05, # heatmap body width
                heatmap_height = unit(h_ipmsHm / 1.6, "mm"),
                heatmap_legend_param = list(title_gp = gpar(fontsize = fl), 
                                            border = "gray10",
                                            border_gp = gpar(lwd = 0.5)))

@@

hm1b_loose <- Heatmap(baitdata_150_loose$mat, 
                      cluster_rows = FALSE, 
                      cluster_columns = FALSE, 
                      col = makeHeatmapCol(stringency = "low"), 
                      border = TRUE, 
                      border_gp = gpar(lwd = 0.5),
                      name = "Mod.\nt-stat.", 
                      na_col = binary_heatmap_colors["FALSE"],
                      column_title = paste(c("150 mM NaCl IP-MS", rep(" ", 45)), collapse = ""),
                      row_title = "Transcription factors",
                      column_title_gp = gpar(fontsize = fl + 3, fontface = "bold"),
                      row_title_gp = gpar(fontsize = fl),
                      column_names_gp = gpar(fontsize = fs),
                      row_names_gp = gpar(fontsize = fs),
                      show_row_names = FALSE, show_column_names = FALSE,
                      use_raster = FALSE, show_heatmap_legend = TRUE, 
                      left_annotation = makeComplexAndDBDAnnotation(
                          baitdata_150_loose$mat, 
                          complexes[c("MBF transcription complex", 
                                      "CCAAT-binding factor complex",
                                      "Atf1-Pcr1")],
                          dbd = dbd, 
                          idmap = idmap),
                      top_annotation = makeTFIntAnnotation(baitdata_150_loose), 
                      bottom_annotation = makeColLabels(baitdata_150_loose$mat, 
                                                        c("Ntu1_plate", "Ntu2_plate", 
                                                          "Esc1_tube", "SPAC3F10.12c_plate"), fl),
                      width = unit(w_ipmsHm, "mm") / 1.05, # heatmap body width
                      heatmap_height = unit(h_ipmsHm / 1.6, "mm"), 
                      heatmap_legend_param = list(title_gp = gpar(fontsize = fl), 
                                                  border = "gray10",
                                                  border_gp = gpar(lwd = 0.5)))

@@

hm1b2 <- Heatmap(baitdata_500$mat, 
                 cluster_rows = FALSE, 
                 cluster_columns = FALSE, 
                 col = makeHeatmapCol(stringency = "high"), 
                 border = TRUE, 
                 border_gp = gpar(lwd = 0.5),
                 name = "Mod.\nt-stat.", 
                 na_col = binary_heatmap_colors["FALSE"],
                 column_title = paste(c("500 mM NaCl IP-MS", rep(" ", 45)), collapse = ""),
                 row_title = "Transcription factors",
                 column_title_gp = gpar(fontsize = fl + 3, fontface = "bold"),
                 row_title_gp = gpar(fontsize = fl),
                 column_names_gp = gpar(fontsize = fs),
                 row_names_gp = gpar(fontsize = fs),
                 show_row_names = FALSE, show_column_names = FALSE,
                 use_raster = FALSE, show_heatmap_legend = TRUE,
                 left_annotation = makeComplexAndDBDAnnotation(
                     baitdata_500$mat, 
                     complexes[c("MBF transcription complex", 
                                 "CCAAT-binding factor complex", "Atf1-Pcr1")], 
                     dbd = dbd, idmap = idmap),
                 top_annotation = makeTFIntAnnotation(baitdata_500), 
                 bottom_annotation = makeColLabels(baitdata_500$mat, 
                                                   c("Ntu1_plate", "Ntu2_plate",
                                                     "Esc1_plate", "SPAC3F10.12c_plate"), fl),
                 width = unit(w_ipmsHm, "mm") / 1.05, # heatmap body width
                 heatmap_height = unit(h_ipmsHm / 1.6, "mm"), # whole heatmap height
                 heatmap_legend_param = list(title_gp = gpar(fontsize = fl), 
                                            border = "gray10",
                                            border_gp = gpar(lwd = 0.5)))

@@

```{r}
#| label: pie-bait-summary
#| fig.width: 10
#| fig.height: 3

pies <- cowplot::plot_grid(
    cowplot::plot_grid(pie_bait_150 + theme(legend.position = "none"), 
                       pie_bait_150_loose + theme(legend.position = "none"), 
                       pie_bait_500 + theme(legend.position = "none"),
                       pie_bait_500_loose + theme(legend.position = "none"), nrow = 2),
    get_legend(pie_bait_150 + theme_cowplot(ft) + theme(legend.position = "bottom")),
    ncol = 1, rel_heights = c(2, 0.25)
)
```

>>>>

```{r extract-heatmap-data}
hmdata_150 <- makeHeatmapData(sce = sce150, adjpthr = adjpThreshold, 
                              log2fcthr = log2fcThreshold, conc = 150,
                              idmap = idmap, baitclass = baitclass)
hmdata_150_loose <- makeHeatmapData(sce = sce150, adjpthr = adjpThresholdLoose, 
                                    log2fcthr = log2fcThreshold, conc = 150,
                                    idmap = idmap, baitclass = baitclass)
hmdata_500 <- makeHeatmapData(sce = sce500, adjpthr = adjpThreshold, 
                              log2fcthr = log2fcThreshold, conc = 500,
                              idmap = idmap, baitclass = baitclass)
hmdata_500_loose <- makeHeatmapData(sce = sce500, adjpthr = adjpThresholdLoose, 
                                    log2fcthr = log2fcThreshold, conc = 500,
                                    idmap = idmap, baitclass = baitclass)

baitdata_150 <- makeBaitHeatmapData(sce = sce150, adjpthr = adjpThreshold, 
                                    log2fcthr = log2fcThreshold, 
                                    nbrIntMat = hmdata_150$nbrIntMat, 
                                    nobait = nobait_150, idmap = idmap, 
                                    complexes = complexes)
baitdata_150_loose <- makeBaitHeatmapData(sce = sce150, adjpthr = adjpThresholdLoose, 
                                          log2fcthr = log2fcThreshold, 
                                          nbrIntMat = hmdata_150_loose$nbrIntMat, 
                                          nobait = nobait_150, idmap = idmap, 
                                          complexes = complexes)
baitdata_500 <- makeBaitHeatmapData(sce = sce500, adjpthr = adjpThreshold, 
                                    log2fcthr = log2fcThreshold, 
                                    nbrIntMat = hmdata_500$nbrIntMat, 
                                    nobait = nobait_150, idmap = idmap, 
                                    complexes = complexes)
baitdata_500_loose <- makeBaitHeatmapData(sce = sce500, adjpthr = adjpThresholdLoose, 
                                          log2fcthr = log2fcThreshold, 
                                          nbrIntMat = hmdata_500_loose$nbrIntMat, 
                                          nobait = nobait_150, idmap = idmap, 
                                          complexes = complexes)
```

@@

hm1b <- Heatmap(baitdata_150$mat, 
                cluster_rows = FALSE, 
                cluster_columns = FALSE, 
                col = makeHeatmapCol(stringency = "high"), 
                border = TRUE, 
                border_gp = gpar(lwd = 0.5),
                name = "Mod.\nt-stat.", 
                na_col = binary_heatmap_colors["FALSE"],
                column_title = paste(c("150 mM NaCl IP-MS", rep(" ", 45)), collapse = ""),
                row_title = "Transcription factors",
                column_title_gp = gpar(fontsize = fl + 3, fontface = "bold"),
                row_title_gp = gpar(fontsize = fl),
                column_names_gp = gpar(fontsize = fs),
                row_names_gp = gpar(fontsize = fs),
                show_row_names = FALSE, show_column_names = FALSE,
                use_raster = FALSE, show_heatmap_legend = TRUE, 
                left_annotation = makeComplexAndDBDAnnotation(
                    baitdata_150$mat, 
                    complexes[c("MBF transcription complex", 
                                "CCAAT-binding factor complex",
                                "Atf1-Pcr1")],
                    dbd = dbd, idmap = idmap, 
                    main_colors = main_colors, bg_color = bg_color, 
                    fontsize = fl),
                top_annotation = makeTFIntAnnotation(
                    baitdata_150, na_color = na_color,
                    fontsize_small = fs, fontsize_large = fl), 
                bottom_annotation = makeColLabels(baitdata_150$mat, 
                                                  c("Ntu1_plate", "Ntu2_plate", 
                                                    "Esc1_tube", "SPAC3F10.12c_plate"), fl),
                width = unit(w_ipmsHm, "mm") / 1.05, # heatmap body width
                heatmap_height = unit(h_ipmsHm / 1.6, "mm"),
                heatmap_legend_param = list(title_gp = gpar(fontsize = fl), 
                                            border = "gray10",
                                            border_gp = gpar(lwd = 0.5)))

@@

hm1b_loose <- Heatmap(baitdata_150_loose$mat, 
                      cluster_rows = FALSE, 
                      cluster_columns = FALSE, 
                      col = makeHeatmapCol(stringency = "low"), 
                      border = TRUE, 
                      border_gp = gpar(lwd = 0.5),
                      name = "Mod.\nt-stat.", 
                      na_col = binary_heatmap_colors["FALSE"],
                      column_title = paste(c("150 mM NaCl IP-MS", rep(" ", 45)), collapse = ""),
                      row_title = "Transcription factors",
                      column_title_gp = gpar(fontsize = fl + 3, fontface = "bold"),
                      row_title_gp = gpar(fontsize = fl),
                      column_names_gp = gpar(fontsize = fs),
                      row_names_gp = gpar(fontsize = fs),
                      show_row_names = FALSE, show_column_names = FALSE,
                      use_raster = FALSE, show_heatmap_legend = TRUE, 
                      left_annotation = makeComplexAndDBDAnnotation(
                          baitdata_150_loose$mat, 
                          complexes[c("MBF transcription complex", 
                                      "CCAAT-binding factor complex",
                                      "Atf1-Pcr1")],
                          dbd = dbd, idmap = idmap, 
                          main_colors = main_colors, bg_color = bg_color, 
                          fontsize = fl),
                      top_annotation = makeTFIntAnnotation(
                          baitdata_150_loose, na_color = na_color,
                          fontsize_small = fs, fontsize_large = fl), 
                      bottom_annotation = makeColLabels(baitdata_150_loose$mat, 
                                                        c("Ntu1_plate", "Ntu2_plate", 
                                                          "Esc1_tube", "SPAC3F10.12c_plate"), fl),
                      width = unit(w_ipmsHm, "mm") / 1.05, # heatmap body width
                      heatmap_height = unit(h_ipmsHm / 1.6, "mm"), 
                      heatmap_legend_param = list(title_gp = gpar(fontsize = fl), 
                                                  border = "gray10",
                                                  border_gp = gpar(lwd = 0.5)))

@@

hm1b2 <- Heatmap(baitdata_500$mat, 
                 cluster_rows = FALSE, 
                 cluster_columns = FALSE, 
                 col = makeHeatmapCol(stringency = "high"), 
                 border = TRUE, 
                 border_gp = gpar(lwd = 0.5),
                 name = "Mod.\nt-stat.", 
                 na_col = binary_heatmap_colors["FALSE"],
                 column_title = paste(c("500 mM NaCl IP-MS", rep(" ", 45)), collapse = ""),
                 row_title = "Transcription factors",
                 column_title_gp = gpar(fontsize = fl + 3, fontface = "bold"),
                 row_title_gp = gpar(fontsize = fl),
                 column_names_gp = gpar(fontsize = fs),
                 row_names_gp = gpar(fontsize = fs),
                 show_row_names = FALSE, show_column_names = FALSE,
                 use_raster = FALSE, show_heatmap_legend = TRUE,
                 left_annotation = makeComplexAndDBDAnnotation(
                     baitdata_500$mat, 
                     complexes[c("MBF transcription complex", 
                                 "CCAAT-binding factor complex", "Atf1-Pcr1")], 
                     dbd = dbd, idmap = idmap, 
                     main_colors = main_colors, bg_color = bg_color, 
                     fontsize = fl),
                 top_annotation = makeTFIntAnnotation(
                     baitdata_500, na_color = na_color,
                     fontsize_small = fs, fontsize_large = fl), 
                 bottom_annotation = makeColLabels(baitdata_500$mat, 
                                                   c("Ntu1_plate", "Ntu2_plate",
                                                     "Esc1_plate", "SPAC3F10.12c_plate"), fl),
                 width = unit(w_ipmsHm, "mm") / 1.05, # heatmap body width
                 heatmap_height = unit(h_ipmsHm / 1.6, "mm"), # whole heatmap height
                 heatmap_legend_param = list(title_gp = gpar(fontsize = fl), 
                                            border = "gray10",
                                            border_gp = gpar(lwd = 0.5)))

@@

```{r}
#| label: pie-bait-summary
#| fig.width: 7
#| fig.height: 7

(pies <- cowplot::plot_grid(
    cowplot::plot_grid(pie_bait_150 + theme(legend.position = "none"), 
                       pie_bait_150_loose + theme(legend.position = "none"), 
                       pie_bait_500 + theme(legend.position = "none"),
                       pie_bait_500_loose + theme(legend.position = "none"), nrow = 2),
    get_legend(pie_bait_150 + theme_cowplot(ft) + theme(legend.position = "bottom")),
    ncol = 1, rel_heights = c(2, 0.25)
))
```
